---
title: "World Population"
author: "M. Mili"
date: "24 avril 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Objective

Show on the world map a set of selected countries
based on two selection Criteria

1. Population size

2. Area

The application is running on <https://moezapps.shinyapps.io/WorldPopulation/>

Source code and data are located on <https://github.com/MoezMili/WorldFig>

## Data

The data has been collected from Wikipedia web site
and merged with the provided data set "Population" from googleVis package
and pre-processed into the data frame Wrld

```{r, comment="",echo = FALSE,message=FALSE}
suppressPackageStartupMessages(library(googleVis))
WrldArea <- read.csv("./WrldArea.csv",sep=";",dec=",")
Wrld <- merge(WrldArea,Population[,2:3],by="Country")
Wrld$Area <- Wrld$Area/10^3
Wrld$Population <- Wrld$Population/10^6
```
```{r, comment="",echo = TRUE}
head(Wrld)
```
*Population expressed in **Millions**, Area expressed in **Thousand Squared Km***

## Issues

As shown on the below graph, few countries have a very large population or area
It makes it difficult to fit on a practical selection tool
```{r, echo = FALSE, fig.align='center'}
plot(x=Wrld$Area,y=Wrld$Population,
     main="Population Density",
     xlab="Area in K-Squared Km",
     ylab="Population in Millions")
```

## Solutions

- The sliders scales have been contained to exclude the countries with
extremely large Population or Area.
- However, we let the possibility to the user to catch those countries using a check box.
- When the box is checked, the higher limit of the corresponding slider is inflated by a factor of 10.
```{r, echo = FALSE,fig.width=6, fig.height=4,fig.align='center'}
suppressPackageStartupMessages(library(jpeg))
img <- readJPEG("./SlidersCB.jpg")
plot(c(100, 250), c(300, 450), type = "n", xlab = "", ylab = "",axes=FALSE)
rasterImage(img, 100, 300, 250, 450)
```
